Time Prints of New Physics at Neutrino Telescopes

### 2024-01-05 paper/sections/detector_response.tex

\textbf{\textit{Detector Response and Statistical Treatment}}---In order to simulate the

>>>>

\textbf{\textit{Detector Response and Statistical Treatment}}---Neutrinos produced by SNe do not have sufficient energy to be individually resolved; however, the large number of neutrinos arriving together gives rise to a temporally localized increase in the noise rate of the detector. 
In order to simulate the signal the prreviously described models would produce, we use the \texttt{ASTERIA}~\cite{spencer_griswold_2020_3926835} software.
This program estimates the light yield from low-energy neutrinos in the IceCube Neutrino Observatory.
In order to interface with \texttt{ASTERIA}, we use the \texttt{SNEWPY} packages, which allows us to define custom supernova fluxes.
